---
title: "AdvWorks-Report"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(janitor) #adorntotals
library(stringr) #
library(formattable)
library(DT) #datatable
library(tidyr)
library(dplyr)
library(openxlsx)
library(fedmatch) #
library(readxl)
library(lubridate)
library(pacman)
library(ggplot2)
library(openxlsx)
library(maps)
library(quantmod)
library(resample)
library(tseries)
library(forecast)
library(fpp2)
library(plotly)
library(tibble)

setwd("~/Data/Learn/R_Projects/advworks_collect/")

items<-read.csv("items.csv")

countries<-read.csv("countries.csv")

oh<-read.csv("order_header.csv")

od<-read.csv("order_details.csv")

cus<-read.csv("cutomers.csv")

#------------------------------------------------------------------------------
oh<-
oh %>% mutate(OrderDate=mdy(OrderDate)) %>% 
mutate(month_year=paste0(format(OrderDate,"%b"),"-",year(OrderDate)),
quarter_year=paste0(quarters(OrderDate),"-",year(OrderDate)),
week_month=paste0(format(OrderDate,"%V"),"-",format(OrderDate,"%b")),
days=weekdays(OrderDate),weekn=format(OrderDate,"%V"),
monthn=month(OrderDate),sow=round_date(OrderDate,"week"),years=year(OrderDate)) %>% rename(AddressID= ShipToAddressID,SalesOrderID=SalesOrder_ID)

od<-
od %>%rename(product_id=ProductID) %>%
inner_join(items,by="product_id") %>%
mutate(subtotal=case_when(
UnitPriceDiscount!=0 ~ 
OrderQty*(UnitPrice-(UnitPrice*UnitPriceDiscount)),TRUE ~(OrderQty*UnitPrice)),
dis=case_when(UnitPriceDiscount>0 ~ "Dis", TRUE ~ "-")) 

oh<-
od %>% group_by(SalesOrderID) %>% 
summarize(qty=sum(OrderQty),subtotal=sum(subtotal)) %>%
inner_join(oh,by="SalesOrderID")  %>%
inner_join(countries,by="AddressID") %>%mutate(order_sales=subtotal+TaxAmt+Freight)

oh<-
oh %>% mutate(
  yw=round_date(OrderDate,"week"),
  ym=round_date(OrderDate,"month"),
  yq=round_date(OrderDate,"quarter"))

oh<-
oh %>% mutate(class=factor(case_when(qty>5 ~ "A",qty>4 ~ "B",TRUE ~ "D")))

#-----------------------------------------------------------------------------
yq_totals_dt<-
oh %>% group_by(years,qr=quarters(OrderDate)) %>% summarize(sales=sum(subtotal)) %>% pivot_wider(id_cols = years,names_from = qr,values_from =sales ,values_fill = FALSE) %>% adorn_totals("col") %>% adorn_totals("row") %>% datatable(class="hover row-border",extensions = list(Buttons=TRUE),options = list(dom="Bfrtip",buttons=c("csv","excel","pdf"),columnDefs=list(list(className="dt-center",targets=c(1:6))))) %>% formatCurrency(columns = c(2:6),digits = 2)

ymw_totals<-
oh %>% group_by(years,week_month,days) %>% summarize(sales=sum(subtotal)) %>% 
pivot_wider(id_cols =c(years,week_month) ,names_from = days,values_from =sales ,values_fill = FALSE)%>% 
select(years,week_month,Monday,Tuesday,Wednesday,Thursday,Friday,Saturday,Sunday)%>% adorn_totals("col")

ymw_totals_dt<-
ymw_totals %>% adorn_totals("row")%>%  
  datatable(class = "hover row-border",
extensions = list(Buttons=TRUE,RowGroup=TRUE),
options = list(dom="Bfrtip",buttons=c("csv","excel","pdf"),
rowGroup=list(dataSrc=1),columnDefs=list(list(className="dt-center",targets=1:10),
list(visible=FALSE,targets=1)))) %>% formatCurrency(columns = c(3:10),digits = 2)

ym_totals_chart<-
oh %>% mutate(months=factor(format(OrderDate,"%b"),
levels =c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec") ),
years=factor(years,levels =c(2011,2012,2013,2014) )) %>% 
group_by(months,years) %>% summarize(sales=sum(subtotal)) %>%
ggplot(aes(x=months,y =sales,group =years ,color=years))+
geom_line() +theme_bw()+
scale_fill_brewer(palette = "Set1")

#-------------------------------Search-----------------------------------------
sales_orders_totals<-
oh %>% group_by(SalesOrderID,OrderDate,customer_name,countries) %>%
summarize(qty=sum(qty),subtotal=sum(subtotal),order_sales=sum(order_sales)) 

sales_orders_totals_dt<-
sales_orders_totals %>% 
datatable(filter = "top",class="hover row-border strip",
extensions = list( Buttons=TRUE),
options = list(dom="Bfrtip",buttons=c("excel","csv","pdf"),
columnDefs=list(list(className="dt-center",targets=1:7)))) %>% formatCurrency(columns =c(6,7),digits = 2)

#------------------------------------------------------------------------------

items_categories_class<-
od %>% group_by(subcategories) %>%
summarize(sales=sum(subtotal),pct=(sum(subtotal)/sum(od$subtotal))*100) %>% 
mutate(class=case_when(pct>3 ~ "A",TRUE ~ "B")) %>% 
select(subcategories,class) %>% inner_join(od,by="subcategories") %>%
group_by(class,category_name,subcategories,product_name) %>% 
summarize(sales=comma(sum(subtotal),digits = 2),qty=comma(sum(OrderQty))) %>%
arrange(class,by_group=TRUE)  

items_categories_class_dt<-
items_categories_class %>% 
datatable(class = "hover row-border",
extensions = list(Buttons=TRUE,RowGroup=TRUE),
options = list(dom="Bfrtip",buttons=c("excel","csv","pdf"),
rowGroup=list(dataSrc=c(1,2)),
columnDefs=list(list(className="dt-center",targets=c(1:6)),list(visible=FALSE,targets=c(1,2)))))


items_categories_class_chart<-
items_categories_class %>% group_by(class) %>% summarize(sales=round(sum(sales)/1000000)) %>% ggplot(aes(x="",y=sales,fill = class))+geom_bar(stat = "identity",width = 1)+coord_polar(theta = "y")+theme_void()+geom_text(aes(label = sales),color="white",size=3.5,fontface = "bold",position = position_stack(vjust = 0.6))+scale_fill_brewer(palette = "Set1")+labs(caption = "Total Per Millions.")+theme(plot.caption = element_text(face = "bold",hjust = ))

categories_chart<-
od %>% group_by(category_name) %>% 
summarize(sales=round(sum(subtotal)/1000000,2)) %>% 
ggplot(aes(x="",y=sales,fill=category_name))+
geom_bar(stat = "identity")+coord_polar(theta = "y")+theme_void()+
geom_text(aes(label=sales),color="white",size=4,fontface = "bold",
position = position_stack(vjust = 0.5))+
labs(subtitle = "Total Sales Per Millions.")+scale_fill_brewer(palette = "Set1")


categories_dt<-
od %>% group_by(category_name) %>% summarize(
Qty=comma(sum(OrderQty)),sales=comma(sum(subtotal)),
pct=round(sum(subtotal)/sum(od$subtotal),3)) %>% datatable(class="hover row-border",extensions = list(Buttons=TRUE),options = list(dom="Bfrtip",
buttons=c("csv","excel","pdf"),
columnDefs=list(list(className="dt-center",targets=c(1:4)))))

yr_categories<-
  oh %>% group_by(SalesOrderID,OrderDate) %>% 
  summarize(n()) %>%select(SalesOrderID,OrderDate) %>%
  inner_join(od,by="SalesOrderID") %>%
  mutate(yrs=as.factor(year(OrderDate))) %>%
  group_by(category_name,yrs)%>%
  summarize(sales=sum(subtotal)) %>% 
  arrange(desc(sales),by_group=TRUE)

yr_categories_chart<-
oh %>% group_by(yrs=factor(years),countries) %>% 
summarize(sales=sum(subtotal)) %>% 
ggplot(aes(x=reorder( countries,sales),y=sales,fill=yrs))+
geom_bar(stat = "identity",position = "dodge")+theme_classic()+
labs(x="",y="",subtitle =paste0("Sales: ",
comma(sum(yr_categories$sales)/1000000),"M"," ","| Quantities: ",
comma(sum(sales_orders_totals$qty),digits = 0)),
caption = " ~ Sales Per Millions.")+
theme(axis.text.x = element_text(face = "bold",size = 9,colour = "black"),
axis.text.y = element_text(face = "bold",size = 9,colour = "black"),
plot.caption= element_text(hjust = 0.5,face = "bold.italic"),
plot.subtitle =element_text(color="brown",face = "bold"))


yr_categories_dt<-
yr_categories %>% 
pivot_wider(id_cols = category_name,names_from = yrs,values_from =sales ,values_fill = FALSE) %>% 
adorn_totals("col") %>%adorn_totals("row") %>%  datatable(class = "hover row-border",extensions = list(Buttons=TRUE),
options = list(list(dom="Bfrtip",buttons=c("csv","excel","pdf"),
columnDefs=list(list(className="dt-center",targets=c(1:6)))))) %>%
formatCurrency(columns = c(2:6),digits = 2)

Bikes_subcategories_totals_chart<-
od %>% filter(category_name=="Bikes") %>% 
group_by(subcategories) %>% summarize(sales=sum(subtotal)) %>% 
ggplot(aes(x="",y=sales,fill=subcategories))+
geom_bar(stat = "identity",width = 1)+coord_polar(theta = "y")+
theme_void()+geom_text(aes(label=round(sales/1000000,2)),fontface = "bold",
position = position_stack(vjust = 0.7),size = 5,color="white")+
labs(caption = "~ Sales Per Milions.")+
theme(plot.caption = element_text(face = "bold",size = 9,color="black",hjust = 0))


Bikes_totals_dt<-
od %>% filter(category_name=="Bikes") %>% 
group_by(subcategories) %>%
summarize(Qty=sum(OrderQty),sales=comma(sum(subtotal)),pct=sum(subtotal)/sum(od$subtotal),Orders=n()) %>% datatable(class = "hover row=border",
extensions = list(Buttons=TRUE),options = list(dom="Bfrtip",buttons=c("csv","excel","pdf"),
columnDefs=list(list(className="dt-center",targets=c(1:2))))) %>% formatCurrency(columns = 3,digits = 2) %>% formatPercentage(columns = 4,digits = 2)


#------------------------------------------------------------------------------
countries_totals<-
oh %>% group_by(countries) %>% 
summarize(sales=sum(subtotal),quantities=sum(qty)) %>%
arrange(desc(sales),by_group=TRUE)

countries_total_dt<-
countries_totals %>%adorn_totals("row") %>% 
datatable(class = "hover row-border",
extensions = list(Buttons=TRUE),
options = list(dom="Bfrtip",buttons=c("csv","excel","pdf"),
columnDefs=list(list(className="dt-center",targets=1:3)))) %>% formatCurrency(columns = 2,digits = 2)

countries_totals_chart<-
countries_totals %>% mutate(sales=round(sales/1000000,2)) %>% 
ggplot(aes(x=reorder(countries,sales),y=sales,fill =countries ))+
geom_bar(stat = "identity")+
geom_text(aes(label=sales),size=4,color="white",fontface = "bold",
position = position_stack(vjust = 0.7))+
labs(x="",y="",caption ="~ Total Sales Per Millions")+theme_bw()+
theme(plot.caption = element_text(face = "bold.italic",size = 8,hjust = 0,),
axis.text.x = element_text(face = "bold",size=9,colour = "black"),
axis.text.y = element_text(face = "bold",size=9,colour = "black"))+coord_flip()

#------------------------------------------------------------

# Year
# Last 6 Months:

mn<-oh %>% group_by(ym) %>% summarize(sales=sum(subtotal))

mn_lts<-ts(mn$sales,start = c(2011,6),end =c(2013,12) ,frequency = 12)

mn_ets<-ets(mn_lts)
mn_fets<-forecast(mn_ets,h = 6)

detect_last<-
cbind(mn[c(32:37),] %>% rename(date=ym)
,rownames_to_column(data.frame(mn_fets))) %>% 
mutate(Low=(Lo.80+Lo.95)/2,Hi=(Hi.95+Hi.80)/2)%>% 
select(date,sales,Point.Forecast,Hi,Low)

detect_last_dt<-
detect_last%>% datatable(class="hover row-border",extensions = list(Buttons=TRUE),
options = list(dom="Bfrtip",buttons=c("csv","pdf","excel"),
columnDefs=list(list(className="dt-center",targets=c(1:5))))) %>% 
formatCurrency(columns = c(2:5),digits = 2)


detect_last_ets_chart<-
detect_last %>% pivot_longer(!date,names_to ="cat" ,values_to = "values") %>% filter(cat !="Hi")%>%  mutate(date=as.POSIXct(date)) %>% ggplot(aes(x=date,y=values,color=cat,group=cat))+geom_line(size=0.8)+theme_bw()+labs(x="",y="")+
scale_x_datetime(date_breaks = "month",date_labels = "%b-%y")+theme(axis.text.x = element_text(color="black",face = "bold",size = 9),axis.text.y = element_text(color="black",face = "bold",size = 9))

mn_ar<-auto.arima(mn_lts)
mn_for<-forecast(mn_ar,h = 6)

# Real

mn_rts<-ts(mn$sales,c(2011,6),frequency = 12)
mn_rets<-ets(mn_rts)
mn_rfor<-forecast(mn_rets,h = 12)

Forecast_model<-
cbind(
data.frame(date=seq(as.Date("2014-08-01"),by="month",len=12)
,
rownames_to_column(data.frame(mn_rfor))%>%
rename(Month_Year=rowname) %>% 
mutate(Low=(Lo.80+Lo.95)/2,Hi=(Hi.95+Hi.80)/2) %>% 
select(Point.Forecast,Hi,Low)))

Forecast_model_dt<-
Forecast_model %>% datatable(class="hover row-border",extensions = list(Buttons=TRUE),
options = list(dom="Bfrtip",buttons=c("csv","pdf","excel"),
columnDefs=list(list(className="dt-center",targets=c(1:4))))) %>% 
formatCurrency(columns = c(2:4),digits = 2)


Forecast_model_chart<-
cbind(
data.frame(date=seq(as.Date("2014-08-01"),by="month",len=12)
,Forecast_model[,c("Point.Forecast","Hi","Low")])) %>% mutate(date=as.POSIXct(date)) %>% 
pivot_longer(!date,names_to ="cat" ,values_to = "values") %>%
ggplot(aes(x=date,y=values,color=cat,group=cat))+geom_line(size=0.8)+theme_bw()+labs(x="",y="")+
scale_x_datetime(date_breaks ="month" ,date_labels = "%b-%Y")


```


# Main

## row{data-width=10}
### Sales
```{r}
valueBox(value = comma(sum(ymw_totals$Total)),caption ="Sales" ,color = "#fad390")
```
### Quantities
```{r}
valueBox(value = comma(sum(od$OrderQty)),caption = "Quantites",color = "#fad390")
```

### Orders
```{r}
valueBox(value =comma(sum(count(oh)),0) ,caption = "Orders",color = "#fad390")
```
### Days
```{r}
valueBox(value =comma(oh %>% select(OrderDate) %>% unique() %>% mutate(n=row_number()) %>% summarize(n=max(n)) %>% select(n),0),caption ="Days" ,color = "#fad390")
```



## row{data-hight=400,.tabset}
### Year_Quarters
```{r}
yq_totals_dt
```

### Countries_Sales
```{r}
ggplotly(countries_totals_chart)
```


# Items
## row{data-hight=500,.tabst}
### Categories
```{r}
categories_dt %>% formatPercentage(columns = 4,digits = 2)
```

### Chart
```{r}
categories_chart
```

# Categories_Class
## row{data-hight=500,.tabset}
### Categories_class

```{r}
items_categories_class_dt %>% formatCurrency(columns = 5,digits = 2)
```

### Items_Classes

```{r}
items_categories_class_chart
```



# Categories_Year
## row{.tabset}
###  TBL
```{r}
yr_categories_dt
```


### Chart
```{r}
ggplotly( yr_categories_chart ,width = 1000)
```


# Year_Month

## row{.tabset}

### TBL

```{r}
ymw_totals_dt
```


### Chart

```{r fig.width=14,fig.height=5}
ggplotly(ym_totals_chart,width = 1000)
```

# BIKES_Category
## row{data-hight=500,.tabset}

### TBL
```{r}


Bikes_totals_dt


```



### Chart
```{r}
Bikes_subcategories_totals_chart
```



# Forecast
## {.tabset}
### Last 6 Months
```{r}
detect_last_dt
```

### Last Chart
```{r}
ggplotly(detect_last_ets_chart)
```

### Forecast Next Year
```{r}
Forecast_model_dt
```


### Chart Next Year 
```{r}
ggplotly(Forecast_model_chart,width = 800)
```

